### 2016-11-23 Detector/Detector.tex
Adding more detector stuff

\subsection{ECAL}
\label{sec:CMSLHC_CMS_ecal}
The \ac{ECAL} \cite{cms-jinst} is a hermetic homogeneous calorimeter
made of nearly 70000 lead tungstate (PbWO$_4$) crystals. It has very
good energy resolution ETC ETC. %Lead tungstate crystals were a good 
%choice for the CMS \ac{ECAL}, satisfying the requirements of the 
%LHC and the detector. 
Despite being further away from the interaction
point than the tracker, the materials in other parts of the detector
still need to be radiation hard. In order to be able to place
the calorimeters inside the bore of the solenoid, a compact \ac{ECAL}
had to be constructed, and to provide excellent resolution a 
highly granular system had to be designed. The short radiation
length and small moli\'ere radius of lead tungstate %NEED TO FIND OUT ABOUT THOSE!
combined with its radiation hardness and the short scintillation decay
time in these crystals motivate the choice of lead tungstate.

Figure \ref{fig:CMS_ECAL} shows a schematic of the \ac{ECAL}, indicating
the geometry. The \ac{ECAL} consists of different subsystems. The \ac{EB} 
covers the pseudorapidity range up to $|\eta|<1.479$, with
crystals of $0.0174 \times 0.0174$ in $\eta - \phi$. The \ac{EE}
provides coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$
Each endcap is divided into two halves. In front of the endcaps 
the preshower detector, covering $1.653<|\eta|<2.6$ is a sampling
calorimeter whose main use is to neutral pions in the endcaps. Additionally
it helps electron identification and improves the resolution
of position determination. The preshower consists
of lead radiators to initiate the shower, with silicon sensors
measuring the deposited energy and shower profiles. %Too copied, improve

@@

\subsection{HCAL}
\label{sec:CMSLHC_CMS_hcal}
Figure \ref{fig:CMS_HCAL} shows an illustration of the \ac{HCAL}.

@@

>>>>

The tracker will be upgraded during the extended year-end technical stop in early 2017. %or just replaced?

\subsection{\acl{ECAL}}
\label{sec:CMSLHC_CMS_ecal}
The \ac{ECAL} \cite{cms-jinst} is a hermetic homogeneous calorimeter
made of nearly 76000 lead tungstate (PbWO$_4$) crystals. It has very
good energy resolution, is highly granular and fast-responding, which
are all needed to be able to detect $H\rightarrow \gamma\gamma$ decays.

Despite being further away from the interaction
point than the tracker, the materials in other parts of the detector
still need to be radiation hard. In order to be able to place
the calorimeters inside the bore of the solenoid, a compact \ac{ECAL}
had to be constructed, and to provide excellent resolution a 
highly granular system had to be designed. The lead tungstate crystals have a 
radiation length of 0.89 cm, a Moli\'ere radius of 2.2 cm, and 80\% of the light
from the crystals is emitted in 25 ns. This short radiation
length, small Moli\'ere radius and short scintillation decay time combined
with the radiation hardness of the material motivate the choice of lead tungstate.

%Moliere radius: characteristic constant of a material giving scale of transverse dimenstion
%of fully contained EM showers. It is the radius of a cylinder containing on average 
%90pct of the shower's energy deposition. Related to radiation length as 
%molrad approx 0.0265X0 (Z+1.2) with Z the atomic number.
%Radiation length: mean distance over which a high energy electron
%loses all but 1/e of its energy by bremmstrahlung and 7/9 of th emean free path for pair production by 
%a high energy photon.

When a high energy electron or photon enters a crystal, it starts a
shower producing a cascade of lower energy particles. Electrons lose
energy through bremsstrahlung, with photons undergoing $\Pe^+ \Pe^-$ 
pair production. The shower continues until the photon energy drops below the 
$\Pe^+\Pe^-$ pair production threshold, and ionisation 
starts to dominate for electrons. The shower ionises the crystals, 
which return to their normal state by emitting scintillation light. 
As the crystals are 25.8 radiation lengths long, most of the shower
is contained inside them.

Figure \ref{fig:CMS_ECAL} shows a schematic of the \ac{ECAL}, indicating
the geometry. The \ac{ECAL} consists of different subsystems. The \ac{EB} 
covers the pseudorapidity range up to $|\eta|<1.479$, with
crystals of $0.0174 \times 0.0174$ in $\eta - \phi$. The \ac{EE}
provides coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$
Each endcap is divided into two halves. In front of the endcaps 
the preshower detectors, covering $1.653<|\eta|<2.6$ is a sampling
calorimeter whose main use is to indentify neutral pions in the endcaps. Additionally
it helps electron identification and improves the resolution
of position determination. Each of the two preshower detectors consist
of two layers of lead radiators to initiate the shower, with silicon sensors
placed after each layer of radiators to measure the deposited energy. The 
total thickness of the preshower comprises 3 radiation lenghts.

@@

To preserve the energy resolution, the \ac{ECAL} crystal and
photodetector temperatures need to be kept stable within $\pm 0.05^o$C
as the number of scintillation photons emitted by the crystals,
and the amplification of the photodetectors are temperature dependent.
The nominal operating temperature, $18^o$C, is ensured by 
supplying the detector with water at this temperature.

To record the light yield of the crystals, amplifying photodetectors
need to be used. In the \ac{EB} avalance photodiodes are employed
for this, with vacuum phototriodes used in the \ac{EE}.

The energy resolution of the \ac{ECAL} can be parameterised as in
equation \ref{eqn:ecalres}.

\begin{equation}\label{eqn:ecalres}
\frac{\sigma}{E} = \sqrt{(\frac{S}{\sqrt{E}})^2+(\frac{N}{E})^2+C^2}
\end{equation}

Where $S$ is the stochastic term, $N$ the noise term and $C$ the constant term.
The stochastic term arises from fluctuations in lateral shower containment and 
fluctuations in scintillation, the noise term due to noise from the electronics
and additional particles in the event, and the constant term comes
from calibration errors, and non-uniformity of longitudinal response.

The values of $S$, $N$ and $C$ have been measured in an electron
test-beam, without a magnetic field or material in front of the \ac{ECAL}. These
amounted to $S = 0.028$ GeV$^{0.5}$, $N = 0.12$ GeV, $C= 0.003$.

\subsection{\acl{HCAL}}
\label{sec:CMSLHC_CMS_hcal}
The \ac{ECAL} is surrounded by the \ac{HCAL}, important for the
measurement of the energies of strongly interacting particles. As
the \ac{ECAL} extends out to a radius of 1.77 m and the magnet coil
starting at a radius of 2.95 m the barrel region of the \ac{HCAL} consists
of the \ac{HB}, which sits inside the magnet coil, and the \ac{HO}, sitting outside it, 
to complement the \ac{HB}. The \ac{HB} and \ac{HO}  provide coverage up to $|\eta|<1.3$, 
beyond which they are complemented by the \ac{HE} and the \ac{HF}. The \ac{HE} provides
coverage between $1.3<|\eta|<3$ with the \ac{HF} extending this coverage up to $|\eta| = 5.2$
The locations of the different subcomponents of the \ac{HCAL} are shown
in figure \ref{fig:CMS_HCAL}.

@@

The \ac{HB} is a sampling calorimeter made of brass absorber
plates with
